---
title: "R Notebook"
output: html_notebook
---


```{r}
library(data.table)       #Load all required packages
library(rvest)
library(lubridate)
library(dbplyr)
library(DataComputing)
library(magrittr)
library(Hmisc)
library(party)
library(rpart)

rm(list = ls())            #Clean up environment

```


###Background Information

This dataset contains policy data for 50 US states and DC from 2001 to 2017. Data include information related to state legislation and regulations on nutrition, physical activity, and obesity in settings such as early care and education centers, restaurants, schools, work places, and others. To identify individual bills, use the identifier ProvisionID. A bill or citation may appear more than once because it could apply to multiple health or policy topics, settings, or states. 


```{r}


getwd()                          #Get working directory
setwd("~/Downloads")             #Set working directory 

untidy <-read.csv("CDC_Nutrition__Physical_Activity__and_Obesity_-_Legislation.csv")    #Read file in table format and create a data frame from it

gc(reset=TRUE)                 #Change from data frame to data table
tracemem(untidy)
untidy <- as.data.table(untidy)
gc()


```



```{r}

untidy           #Take a look


```

```{r}

#Clean Data 
#Change variables to start with lowercase/ make easier to use

Legislation <-
  untidy %>%
  rename(year = Year, quarter = Quarter, state = LocationAbbr, healthTopic = HealthTopic, policyTopic = PolicyTopic, dataSource = DataSource, setting = Setting, title = Title, status = Status, citation = Citation, statusAltValue = StatusAltValue, dataType = DataType, comments = Comments, enDate = EnactedDate, effDate = EffectiveDate, coordinates = GeoLocation, display = DisplayOrder)

Legislation



```



## What type of information can we find with this data?

We can see how much legislation has been passed in certain years, which years have been the most progressive, which states have more legislation than others, which topic has been most popular, and more. This information can give government officials the ability to see where certain states need to improve, which topics need to be emphasized, and more.


## Which year passed the most legislation?


```{r}

yearlyData <-
Legislation %>%
  group_by(year) %>%
  summarise(total = sum(year)) %>%
  mutate(total = total/1000)


yearlyData %>%
  ggplot(aes(x=year,y=total ))+
  geom_bar(stat='identity',position='stack', width=.9, fill = "red") +
  ylab("Total (1000s)") +
  xlab("Year") 


```

Each bar in the chart represents one year. One can see that in 2011, the most legislation/regulation has been passed between 2001 and 2017.



## Legislation vs. Regulation by Topic

```{r}

Legislation %>%
  group_by(year, healthTopic, PolicyTypeID) %>%
  summarise(total = sum(year)) %>%
  mutate(total = total/1000) %>%
  ggplot(aes(x= year, y = total)) +
  geom_point(color = "red") +
  facet_grid(PolicyTypeID ~ healthTopic) +
  ylab("total (1000s)") +
  xlab("Year") 



```


As we can see, there has been a lot less regulation than legislation. Nutrititional legislation appears to be the most popular as represented by the many glyphs on the graph. Regulation is less popular and shows little to no type of trend in the graph. In each of the graphs, around 2011 there is peak which corresponds with our finding earlier about 2011 being the most popular year.


## Legislation on a map

```{r}
stateData <-
Legislation %>%
  group_by(state, year) %>%           #sort cases by state and year
  mutate(total = sum(year))        #create new variable total

stateData    #look at data
  
USMap(data = stateData, key = "state", fill = "total")   #plot on a USMap


```

From this graph, we can see that states like New York, California, Washington, and Illnois, and Hawaii are weaker than most when it comes to passing legislation on nutrition, obesity, and physical activity.

## Timeline of Legislation By Setting

```{r}

#sort cases by year, setting, and policy type ID

Legislation %>%
  group_by(year, setting, PolicyTypeID) %>%
  summarise(total = sum(year)) %>%
  mutate(total = total/1000) %>%
  ggplot(aes(x = year, y = total, color = setting)) +
  geom_line() +
  ylab("total (1000s)") +
  facet_wrap(~PolicyTypeID)




```

In this graph we still see a peak in 2011, but we can also now see what the bills were passed for. Community takes the lead in both regulation and legislation. 





















